MLH1 Results Outline

### 2020-02-26 doc/Results.rmd
blah

---
title: "MLH1 Results Outline"
date: 
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '5'
    toc_float: yes
  pdf_document: default
  word_document:
    toc: yes
    toc_depth: '5'
bibliography: refs_Main_Report.bib
---

>>>>

---
title: "MLH1 Results Outline"
date: 
output:
  word_document:
    toc: yes
    toc_depth: '5'
  pdf_document: default
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '5'
    toc_float: yes
bibliography: refs_Main_Report.bib
---
